---
title: "Bubble Trouble: Strageties something something Filterbubble Awareness"
author: "Laura Burbach, Patrick Halbach, Martina Ziefle, André Calero Valdez"
date: "12 12 2018"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
    collapsed: false
    df_print: paged
    dev: png
    self_contained: true
    number_sections: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sjlabelled)
library(sjPlot)
library(forcats)
library(corrplot)
library(hcictools)
library(ggplot2)
library(likert)
library(apastats)
library(apaTables)
library(psych)
library(ggthemes)
library(scales)
library(jmv)
library(papaja)

source("../survemonky_helper.R")
source("../helpers.R")
```

# Data Cleaning
First we clean our SPSS output files. For this purpose we remove identifying information..

```{r data-cleaning, include=FALSE}
raw <- haven::read_sav("data/raw.sav", encoding = "UTF-8")


# rename variables ---- 
codebook_filename <- "codebook.csv"

# If file does not exist
if(!file.exists(codebook_filename)){
  variable_names <- names(raw)
  label_names <- get_label(raw)

  codebook <- data.frame(variable_names, label_names)
  print("test")
  write_delim(codebook, path = codebook_filename, delim = ";")
} else {
  codebook <-read_delim(codebook_filename, delim=";")
}

# Change variable labels to those from the codebook.csv
names(raw) <- codebook$variable_names

names(raw)

# select required variables ----
raw[,c(-1:-10)] %>% select(-starts_with("p0")) -> data

# factors and ordinal data
data$age <- as.numeric(data$age)
data$gender

data$education <- factor(data$education, 
                         labels=get_labels(data$education), 
                         level = 1:7, ordered = T)


data <- data %>% mutate_at(vars(starts_with("big5")), srvmky_convert_factor, rev = T )
#data <- data %>% mutate_at(vars(starts_with("FB_")), srvmky_convert_factor, rev = T ) 
data <- data %>% mutate_at(vars(starts_with("FBV_")), srvmky_convert_factor, rev = T )

# filter incomplete responses
# data %>% filter(rowSums(is.na(data)) < 5)


codebook[16:25,]$label_names
# calculate factors and scales

agreement_english <- function(x) {
  factor(x, levels = c("Stimme gar nicht zu",
                            "Stimme nicht zu",
                            "Stimme eher nicht zu",
                            "Stimme eher zu",
                            "Stimme zu",
                            "Stimme vollkommen zu"),
              labels = c("completely disagree",
                         "disagree",
                         "rather disagree",
                         "rather agree",
                         "agree",
                         "completely agree"))
}

```


## Calculation of scales


### Calculate Big 5
```{r scale_big5}

# create big 5 factors ----  
key_list_big5 <- list(b5_n = list("-big5_04", "big5_09"),
                      b5_e = list("-big5_01", "big5_06"),
                      b5_o = list("big5_05", "big5_10"),
                      b5_a = list("big5_02", "-big5_07"),
                      b5_c = list("-big5_03", "big5_08"))

scores <- psych::scoreItems(key_list_big5, data, min = 1, max = 6, impute = "mean")  

scores

data <- data %>% cbind(scores$scores) 

#data <- data %>% select(-starts_with("big5"))


```


### Facebook
```{r scale_facebook}

key_list_FB <- list(FB = list("FiB_schon_gehört", "FiB_glaube_existiert", "FiB_betrifft_persönlich", "FiB_Problem", "FiB_interessante_Beiträge", "FiB_bewusstes_Vorgehen"))

scores <- psych::scoreItems(key_list_FB, data, min = 1, max = 6, impute = "mean")  

scores

# Attach scale
data <- data %>% cbind(scores$scores) 

# Remove items
# data <- data %>% select(-starts_with("FB_"))



```


### Avoidance Strategies
```{r scale_fbv}

key_list_FBV <-
  list(
  FBV = list(
  "FBV_Loeschen",
  "FBV_Incognito",
  "FBV_Vielfalt_erzwingen",
  "FBV_Explorer",
  "FBV_deabonnieren"
  )
  )

scores <- psych::scoreItems(key_list_FBV, data, min = 1, max = 6, impute = "mean")

scores

data <- data %>% cbind(scores$scores) 

# data <- data %>% select(-starts_with("FBV_"))

data

```

# Analysis
Here we compute the results

## Descriptive Statistics
```{r descriptive}
psych::describe(data)
```


### Awareness of the filter bubble
Here we look at the awareness of the filter bubble
```{r Awareness Filter bubble}

library(purrr)

variable_set <- c(
            "FiB_schon_gehört",
            "FiB_glaube_existiert",
            "FiB_interessante_Beiträge",
            "FiB_betrifft_persönlich",
            "FiB_Problem",
            "FiB_bewusstes_Vorgehen"
            )

label_set <- c(
              "heard about the filter bubbles",
              "believe the filter bubble exists",
              "filter bubble displays only interesting posts",
              "filter bubble affects me personally",
              "filer bubble is a problem",
              "take action against the filter bubble"
              )

make_variable_labels <- function(x) {
  factor(x, levels = variable_set,
            labels = label_set
            )
}

data %>% 
  dplyr::select(variable_set) %>% 
  map_df(as.numeric) %>% 
  psych::describe() %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  mutate (variablename = make_variable_labels(rowname)) -> plot_data

library(hcictools)
library(RColorBrewer)

rwthcolors <- hcictools::rwth.colorpalette()

agreement_palette <- colorRampPalette(c(rwthcolors$red,"white", rwthcolors$green))

plot_data %>% 
  ggplot() +
  aes(x=reorder(variablename, mean), y = 6 - mean, fill = reorder(variablename, mean), 
      ymin = 6 - mean - se * 1.96 , ymax = 6 - mean + se * 1.96) +
  scale_y_continuous(limits = c(0,5), labels = 1:6) +
  geom_col(width = 0.7) +
  geom_errorbar(width = 0.3) +
  labs(x="Variables", y="Means of agreement (1-6)", 
       title="Most users know the pheonomenon filter bubble",
       subtitle = "Different measures of filter bubble awareness",
       caption = "Errorbars denote the 95% confidence interval of the mean.") +
  guides(fill = FALSE) +
  coord_flip() +
  #scale_fill_brewer(palette = "Spectral") + 
  scale_fill_manual(values=agreement_palette(6)) +
  theme_bw() + 
  NULL


ggsave("Filterbubbles.pdf",  width = 7, height = 3)

```


###```{r Likert Example}

#data %>% 
#  dplyr::select(variable_set) %>% 
# magrittr::set_colnames(label_set) %>%
#  mutate_all(agreement_english) %>% 
#  likert() %>% plot(low.color = rwthcolors$red, high.color = rwthcolors$green) + 
#  labs(title="Test")

#```


### Prevention strategies against the filter bubble
Here we look at prevention strategies against the filter bubble
```{r Prevention Strategies}
variable_set2 <- c(
  "FBV_Loeschen",
  "FBV_Incognito",
  "FBV_Vielfalt_erzwingen",
  "FBV_Explorer",
  "FBV_deabonnieren"
)

label_set2 <- c(
  "clear browser history",
  "use Incognito function",
  "click/like different posts",
  "use Explore-Button",
  "subscribe to pages/friends"
)

make_variable_labels <- function(x) {
  factor(x, levels = variable_set2,
            labels = label_set2
            )
}

data %>% 
  dplyr::select(variable_set2) %>% 
  map_df(as.numeric) %>% 
  psych::describe() %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  mutate (variablename = make_variable_labels(rowname)) -> plot_data

#rwthcolors <- hcictools::rwth.colorpalette()

#agreement_palette <- colorRampPalette(c(rwthcolors$red,"white", rwthcolors$green))

plot_data %>% 
  ggplot() +
  aes(x=reorder(variablename, mean), y = mean - 1, fill = reorder(variablename, mean), 
      ymin = mean - 1 - se * 1.96 , ymax = mean - 1 + se * 1.96) +
  scale_y_continuous(limits = c(0,5), labels = 1:6) +
  geom_col(width = 0.8) +
  geom_errorbar(width = 0.3) +
  labs(x="Variables", y="Means of agreement (1-6)", 
       title="The most commonly used strategy is clearing browser history",
       subtitle = "Different avoidance strategies against filterbubbles",
       caption = "Errorbars denote the 95% confidence intervall of the mean.") +
  guides(fill = FALSE) +
  coord_flip() +
  #scale_fill_brewer(palette = "Spectral") + 
  scale_fill_manual(values=agreement_palette(6)) +
  theme_bw() + 
  NULL

ggsave("preventionStrategies.pdf", width = 7, height = 3)

```

### Big Five Personality
Here we look at the Big Five personality frequencies of the participants
```{r Big Five}
variable_set3 <- c(
  "b5_n",
  "b5_e",
  "b5_o",
  "b5_a",
  "b5_c"
)

label_set3 <- c(
  "neuroticism",
  "extraversion",
  "openness",
  "agreeableness",
  "conscientiousness"
)

make_variable_labels <- function(x) {
  factor(x, levels = variable_set3,
            labels = label_set3
            )
}

data %>% 
  dplyr::select(variable_set3) %>% 
  map_df(as.numeric) %>% 
  psych::describe() %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  mutate (variablename = make_variable_labels(rowname)) -> plot_data

library(hcictools)
library(RColorBrewer)

rwthcolors <- hcictools::rwth.colorpalette()

agreement_palette <- colorRampPalette(c(rwthcolors$red,"white", rwthcolors$green))

plot_data %>% 
  ggplot() +
  aes(x=reorder(variablename, mean), y = mean - 1, fill = reorder(variablename, mean), 
      ymin = mean - 1 - se * 1.96 , ymax = mean - 1 + se * 1.96) +
  scale_y_continuous(limits = c(0,5), labels = 1:6) +
  geom_col(width = 0.8) +
  geom_errorbar(width = 0.3) +
  labs(x="Variables", y="Means of agreement (1-6)", 
       title="Participants are open-minded",
       subtitle = "Big Five personality traits",
       caption = "Errorbars denote the 95% confidence intervall of the mean.") +
  guides(fill = FALSE) +
  #coord_flip() +
  scale_fill_brewer(palette = "Spectral") + 
  #scale_fill_manual(values=agreement_palette(6)) +
  theme_bw() + 
  NULL

ggsave("BigFive.pdf", width = 6, height = 4)

```

### Reasons to use Facebook
Here we look at frequencies of the Facebook usage motives
```{r Facebook usage motives}

variable_set4 <- c(
  "fb_um_friends",
  "fb_um_newfriends",
  "fb_um_job",
  "fb_um_mich_informieren",
  "fb_um_andere_informieren",
  "fb_um_Meinung_zu_äußern"
)


label_set4 <- c(
  "friends",
  "new friends",
  "job",
  "my information",
  "others information",
  "opinion expression"
)

make_variable_labels <- function(x) {
  factor(x, levels = variable_set4,
            labels = label_set4
            )
}

data %>% 
  dplyr::select(variable_set4) %>% 
  map_df(as.numeric) %>% 
  psych::describe() %>% 
  as.data.frame() %>% 
  rownames_to_column() %>% 
  mutate (variablename = make_variable_labels(rowname)) -> plot_data

library(hcictools)
library(RColorBrewer)

rwthcolors <- hcictools::rwth.colorpalette()

agreement_palette <- colorRampPalette(c(rwthcolors$red,"white", rwthcolors$green))

plot_data %>% 
  ggplot() +
  aes(x=reorder(variablename, mean), y = 6 - mean, fill = reorder(variablename, mean), 
      ymin = 6 - mean - se * 1.96 , ymax = 6 - mean + se * 1.96) +
  scale_y_continuous(limits = c(0,5), labels = 1:6) +
  geom_col(width = 0.5) +
  geom_errorbar(width = 0.3) +
  labs(x="Variables", y="Means of agreement (1-6)", 
       title="Participants use Facebook primarily to stay in touch with friends",
       subtitle = "Different reasons to use Facebook for",
       caption = "Errorbars denote the 95% confidence intervall of the mean.") +
  guides(fill = FALSE) +
  #coord_flip() +
  scale_fill_brewer(palette = "Spectral") + 
  #scale_fill_manual(values=agreement_palette(6)) +
  theme_bw() + 
  NULL

ggsave("Facebook usage motives.pdf", width = 6, height = 4)

```


### Gender Differences for Personality
```{r analysis}
## means

formatting_option <- "pandoc" # or "latex"

apa_ttest <- function(formula, data, type = formatting_option, alpha = 0.05) {
  hypo <- t.test(formula, data = data)

  stat_output <-  apastats::describe.ttest(hypo, type = type)
  
  if(hypo$p.value < alpha){
    msg <- paste0("Es gibt einen signifikanten Unterschied (",stat_output,").")
  } else {
    msg <- paste0("Es gibt keinen signifikanten Unterschied (",stat_output,").")
  }
  
  msg
}


  data %>% apa_ttest(formula = b5_n ~ gender)
  data %>% apa_ttest(formula = b5_o ~ gender)
  data %>% apa_ttest(formula = b5_c ~ gender)
  data %>% apa_ttest(formula = b5_e ~ gender)
  data %>% apa_ttest(formula = b5_a ~ gender)

```

Unterschied: zwischen Geschlechtern für Offenheit: `r data %>% apa_ttest(formula = b5_o ~ gender)`

## ANOVA Test

```{r anova}

jmv::ttestIS(data, (c("b5_n", "b5_e", "b5_c")), group = "gender", welchs = T, norm = T)

result <- jmv::ANOVA(data = data, 
                     dep = c("b5_o"), 
                     factors = "education", 
                     emmPlots = T, 
                     emMeans = list("education"))


model <- aov(data = data, b5_n ~ education)
m<- anova(model)



data %>% select(starts_with("b5"), "FBV", starts_with("fb")) %>% select(1:10) %>% 
  mutate_if(is.ordered, as.numeric) %>% 
  hcictools::cor.matrix.plot()


data %>% select(starts_with("b5"), "FBV", starts_with("fb")) %>% select(1:10) %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ b5_n + fb_tablet) -> hypo_c1

apastats::describe.r(hypo_c1, type="latex")

lm(data = corrdata, formula = fb_tablet ~ b5_n) -> hypo_lm1
lm(data = corrdata, formula = fb_tablet ~ b5_n + fb_smartphone) -> hypo_lm2

anova(hypo_lm1, hypo_lm2)

apastats::describe.glm(hypo_lm2, type="latex")

psych::alpha(corrdata, list("b5_o", "b5_n", "b5_c"))

#library(likert)
#data %>% select(6:15) %>% likert() %>% plot()

```



### age


### Awareness of filter bubbles and Action against filter bubbles
Here we look at the relationship between the awareness of filter bubbles and possible avoidannce strategies against filter bubbles
```{r Awareness and avoidance strategies}

data %>%  select(starts_with("FiB"), "FBV_Loeschen", "FBV_Incognito", "FBV_Vielfalt_erzwingen", "FBV_Explorer", "FBV_deabonnieren") %>% 
  mutate_if(is.ordered, as.numeric) %>% 
  hcictools::cor.matrix.plot() #%>% apa.cor.table() %>% a_table()

data2 <- data %>% select(starts_with("FiB"), "FBV_Loeschen", "FBV_Incognito", "FBV_Vielfalt_erzwingen", "FBV_Explorer", "FBV_deabonnieren")

#print(apa.cor.table(data2, filename = NA, table.number = NA, show.conf.interval = TRUE, landscape = TRUE), type='latex')

AA_table <- data %>% select(starts_with("FiB"), "FBV_Loeschen", "FBV_Incognito", "FBV_Vielfalt_erzwingen", "FBV_Explorer", "FBV_deabonnieren") %>% mutate_if(is.ordered, as.numeric) %>% apa.cor.table() %>% a_table()



data %>% select(starts_with("FiB"), "FBV_Loeschen", "FBV_Incognito", "FBV_Vielfalt_erzwingen", "FBV_Explorer", "FBV_deabonnieren") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ FiB_schon_gehört + FBV_Loeschen) -> hypo_c1
cor.test(data = corrdata, ~ FiB_schon_gehört + FBV_Incognito) -> hypo_c2
cor.test(data = corrdata, ~ FiB_schon_gehört + FBV_Vielfalt_erzwingen) -> hypo_c3
cor.test(data = corrdata, ~ FiB_schon_gehört + FBV_Explorer) -> hypo_c4
cor.test(data = corrdata, ~ FiB_schon_gehört + FBV_deabonnieren) -> hypo_c5

cor.test(data = corrdata, ~ FiB_glaube_existiert + FBV_Loeschen) -> hypo_c6
cor.test(data = corrdata, ~ FiB_glaube_existiert + FBV_Incognito) -> hypo_c7
cor.test(data = corrdata, ~ FiB_glaube_existiert + FBV_Vielfalt_erzwingen) -> hypo_c8
cor.test(data = corrdata, ~ FiB_glaube_existiert + FBV_Explorer) -> hypo_c9
cor.test(data = corrdata, ~ FiB_glaube_existiert + FBV_deabonnieren) -> hypo_c10

cor.test(data = corrdata, ~ FiB_betrifft_persönlich + FBV_Loeschen) -> hypo_c11
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + FBV_Incognito) -> hypo_c12
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + FBV_Vielfalt_erzwingen) -> hypo_c13
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + FBV_Explorer) -> hypo_c14
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + FBV_deabonnieren) -> hypo_c15

cor.test(data = corrdata, ~ FiB_Problem + FBV_Loeschen) -> hypo_c16
cor.test(data = corrdata, ~ FiB_Problem + FBV_Incognito) -> hypo_c17
cor.test(data = corrdata, ~ FiB_Problem + FBV_Vielfalt_erzwingen) -> hypo_c18
cor.test(data = corrdata, ~ FiB_Problem + FBV_Explorer) -> hypo_c19
cor.test(data = corrdata, ~ FiB_Problem + FBV_deabonnieren) -> hypo_c20

cor.test(data = corrdata, ~ FiB_interessante_Beiträge + FBV_Loeschen) -> hypo_c21
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + FBV_Incognito) -> hypo_c22
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + FBV_Vielfalt_erzwingen) -> hypo_c23
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + FBV_Explorer) -> hypo_c24
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + FBV_deabonnieren) -> hypo_c25

cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + FBV_Loeschen) -> hypo_c26
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + FBV_Incognito) -> hypo_c27
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + FBV_Vielfalt_erzwingen) -> hypo_c28
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + FBV_Explorer) -> hypo_c29
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + FBV_deabonnieren) -> hypo_c30

apastats::describe.r(hypo_c1, type="latex")
apastats::describe.r(hypo_c2, type="latex")
apastats::describe.r(hypo_c3, type="latex")
apastats::describe.r(hypo_c4, type="latex")
apastats::describe.r(hypo_c5, type="latex")

apastats::describe.r(hypo_c6, type="latex")
apastats::describe.r(hypo_c7, type="latex")
apastats::describe.r(hypo_c8, type="latex")
apastats::describe.r(hypo_c9, type="latex")
apastats::describe.r(hypo_c10, type="latex")

apastats::describe.r(hypo_c11, type="latex")
apastats::describe.r(hypo_c12, type="latex")
apastats::describe.r(hypo_c13, type="latex")
apastats::describe.r(hypo_c14, type="latex")
apastats::describe.r(hypo_c15, type="latex")

apastats::describe.r(hypo_c16, type="latex")
apastats::describe.r(hypo_c17, type="latex")
apastats::describe.r(hypo_c18, type="latex")
apastats::describe.r(hypo_c19, type="latex")
apastats::describe.r(hypo_c20, type="latex")

apastats::describe.r(hypo_c21, type="latex")
apastats::describe.r(hypo_c22, type="latex")
apastats::describe.r(hypo_c23, type="latex")
apastats::describe.r(hypo_c24, type="latex")
apastats::describe.r(hypo_c25, type="latex")

apastats::describe.r(hypo_c26, type="latex")
apastats::describe.r(hypo_c27, type="latex")
apastats::describe.r(hypo_c28, type="latex")
apastats::describe.r(hypo_c29, type="latex")
apastats::describe.r(hypo_c30, type="latex")

lm(data = corrdata, formula = FiB_schon_gehört ~ FBV_Loeschen) -> hypo_lm1
lm(data = corrdata, formula = FiB_schon_gehört ~ FBV_Incognito) -> hypo_lm2
lm(data = corrdata, formula = FiB_schon_gehört ~ FBV_Incognito) -> hypo_lm3
lm(data = corrdata, formula = FiB_schon_gehört ~ FBV_Incognito) -> hypo_lm4
lm(data = corrdata, formula = FiB_schon_gehört ~ FBV_Incognito) -> hypo_lm5


```

### Facebook usage motives and awareness of filter bubbles
Here we look at the relationship between the Facebook usage motives and the awareness of filter bubbles 
```{r Facebook usage motives abd awareness of filter bubbles}
data %>% select(starts_with("FiB"), "fb_um_friends", "fb_um_newfriends", "fb_um_job", "fb_um_mich_informieren", "fb_um_andere_informieren", "fb_um_Meinung_zu_äußern") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ FiB_schon_gehört + fb_um_friends) -> hypo_c102
cor.test(data = corrdata, ~ FiB_schon_gehört + fb_um_newfriends) -> hypo_c103
cor.test(data = corrdata, ~ FiB_schon_gehört + fb_um_job) -> hypo_c104
cor.test(data = corrdata, ~ FiB_schon_gehört + fb_um_mich_informieren) -> hypo_c105
cor.test(data = corrdata, ~ FiB_schon_gehört + fb_um_andere_informieren) -> hypo_c106
cor.test(data = corrdata, ~ FiB_schon_gehört + fb_um_Meinung_zu_äußern) -> hypo_c107

cor.test(data = corrdata, ~ FiB_glaube_existiert + fb_um_friends) -> hypo_c108
cor.test(data = corrdata, ~ FiB_glaube_existiert + fb_um_newfriends) -> hypo_c109
cor.test(data = corrdata, ~ FiB_glaube_existiert + fb_um_job) -> hypo_c110
cor.test(data = corrdata, ~ FiB_glaube_existiert + fb_um_mich_informieren) -> hypo_c111
cor.test(data = corrdata, ~ FiB_glaube_existiert + fb_um_andere_informieren) -> hypo_c112
cor.test(data = corrdata, ~ FiB_glaube_existiert + fb_um_Meinung_zu_äußern) -> hypo_c113

cor.test(data = corrdata, ~ FiB_betrifft_persönlich + fb_um_friends) -> hypo_c114
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + fb_um_newfriends) -> hypo_c115
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + fb_um_job) -> hypo_c116
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + fb_um_mich_informieren) -> hypo_c117
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + fb_um_andere_informieren) -> hypo_c118
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + fb_um_Meinung_zu_äußern) -> hypo_c119

cor.test(data = corrdata, ~ FiB_Problem + fb_um_friends) -> hypo_c120
cor.test(data = corrdata, ~ FiB_Problem + fb_um_newfriends) -> hypo_c121
cor.test(data = corrdata, ~ FiB_Problem + fb_um_job) -> hypo_c122
cor.test(data = corrdata, ~ FiB_Problem + fb_um_mich_informieren) -> hypo_c123
cor.test(data = corrdata, ~ FiB_Problem + fb_um_andere_informieren) -> hypo_c124
cor.test(data = corrdata, ~ FiB_Problem + fb_um_Meinung_zu_äußern) -> hypo_c125

cor.test(data = corrdata, ~ FiB_interessante_Beiträge + fb_um_friends) -> hypo_c126
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + fb_um_newfriends) -> hypo_c127
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + fb_um_job) -> hypo_c128
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + fb_um_mich_informieren) -> hypo_c129
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + fb_um_andere_informieren) -> hypo_c130
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + fb_um_Meinung_zu_äußern) -> hypo_c131

cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + fb_um_friends) -> hypo_c132
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + fb_um_newfriends) -> hypo_c133
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + fb_um_job) -> hypo_c134
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + fb_um_mich_informieren) -> hypo_c135
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + fb_um_andere_informieren) -> hypo_c136
cor.test(data = corrdata, ~ FiB_bewusstes_Vorgehen + fb_um_Meinung_zu_äußern) -> hypo_c137

apastats::describe.r(hypo_c102, type="latex")
apastats::describe.r(hypo_c103, type="latex")
apastats::describe.r(hypo_c104, type="latex")
apastats::describe.r(hypo_c105, type="latex")
apastats::describe.r(hypo_c106, type="latex")
apastats::describe.r(hypo_c107, type="latex")

apastats::describe.r(hypo_c108, type="latex")
apastats::describe.r(hypo_c109, type="latex")
apastats::describe.r(hypo_c110, type="latex")
apastats::describe.r(hypo_c111, type="latex")
apastats::describe.r(hypo_c112, type="latex")
apastats::describe.r(hypo_c113, type="latex")

apastats::describe.r(hypo_c114, type="latex")
apastats::describe.r(hypo_c115, type="latex")
apastats::describe.r(hypo_c116, type="latex")
apastats::describe.r(hypo_c117, type="latex")
apastats::describe.r(hypo_c118, type="latex")
apastats::describe.r(hypo_c119, type="latex")

apastats::describe.r(hypo_c120, type="latex")
apastats::describe.r(hypo_c121, type="latex")
apastats::describe.r(hypo_c122, type="latex")
apastats::describe.r(hypo_c123, type="latex")
apastats::describe.r(hypo_c124, type="latex")
apastats::describe.r(hypo_c125, type="latex")

apastats::describe.r(hypo_c126, type="latex")
apastats::describe.r(hypo_c127, type="latex")
apastats::describe.r(hypo_c128, type="latex")
apastats::describe.r(hypo_c129, type="latex")
apastats::describe.r(hypo_c130, type="latex")
apastats::describe.r(hypo_c131, type="latex")

apastats::describe.r(hypo_c132, type="latex")
apastats::describe.r(hypo_c133, type="latex")
apastats::describe.r(hypo_c134, type="latex")
apastats::describe.r(hypo_c135, type="latex")
apastats::describe.r(hypo_c136, type="latex")
apastats::describe.r(hypo_c137, type="latex")
```


### Reasons to use Facebook and Action against filter bubbles
```{r Reasons to use Facebook and avoidance strategies}
data %>% select(starts_with("fb_um"), "FBV_Loeschen", "FBV_Incognito", "FBV_Vielfalt_erzwingen", "FBV_Explorer", "FBV_deabonnieren") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ fb_um_friends + FBV_Loeschen) -> hypo_c31
cor.test(data = corrdata, ~ fb_um_friends + FBV_Incognito) -> hypo_c32
cor.test(data = corrdata, ~ fb_um_friends + FBV_Vielfalt_erzwingen) -> hypo_c33
cor.test(data = corrdata, ~ fb_um_friends + FBV_Explorer) -> hypo_c34
cor.test(data = corrdata, ~ fb_um_friends + FBV_deabonnieren) -> hypo_c35

cor.test(data = corrdata, ~ fb_um_newfriends + FBV_Loeschen) -> hypo_c36
cor.test(data = corrdata, ~ fb_um_newfriends + FBV_Incognito) -> hypo_c37
cor.test(data = corrdata, ~ fb_um_newfriends + FBV_Vielfalt_erzwingen) -> hypo_c38
cor.test(data = corrdata, ~ fb_um_newfriends + FBV_Explorer) -> hypo_c39
cor.test(data = corrdata, ~ fb_um_newfriends + FBV_deabonnieren) -> hypo_c40

cor.test(data = corrdata, ~ fb_um_job + FBV_Loeschen) -> hypo_c41
cor.test(data = corrdata, ~ fb_um_job + FBV_Incognito) -> hypo_c42
cor.test(data = corrdata, ~ fb_um_job + FBV_Vielfalt_erzwingen) -> hypo_c43
cor.test(data = corrdata, ~ fb_um_job + FBV_Explorer) -> hypo_c44
cor.test(data = corrdata, ~ fb_um_job + FBV_deabonnieren) -> hypo_c45

cor.test(data = corrdata, ~ fb_um_mich_informieren + FBV_Loeschen) -> hypo_c46
cor.test(data = corrdata, ~ fb_um_mich_informieren + FBV_Incognito) -> hypo_c47
cor.test(data = corrdata, ~ fb_um_mich_informieren + FBV_Vielfalt_erzwingen) -> hypo_c48
cor.test(data = corrdata, ~ fb_um_mich_informieren + FBV_Explorer) -> hypo_c49
cor.test(data = corrdata, ~ fb_um_mich_informieren + FBV_deabonnieren) -> hypo_c50

cor.test(data = corrdata, ~ fb_um_andere_informieren + FBV_Loeschen) -> hypo_c51
cor.test(data = corrdata, ~ fb_um_andere_informieren + FBV_Incognito) -> hypo_c52
cor.test(data = corrdata, ~ fb_um_andere_informieren + FBV_Vielfalt_erzwingen) -> hypo_c53
cor.test(data = corrdata, ~ fb_um_andere_informieren + FBV_Explorer) -> hypo_c54
cor.test(data = corrdata, ~ fb_um_andere_informieren + FBV_deabonnieren) -> hypo_c55

cor.test(data = corrdata, ~ fb_um_Meinung_zu_äußern + FBV_Loeschen) -> hypo_c56
cor.test(data = corrdata, ~ fb_um_Meinung_zu_äußern + FBV_Incognito) -> hypo_c57
cor.test(data = corrdata, ~ fb_um_Meinung_zu_äußern + FBV_Vielfalt_erzwingen) -> hypo_c58
cor.test(data = corrdata, ~ fb_um_Meinung_zu_äußern + FBV_Explorer) -> hypo_c59
cor.test(data = corrdata, ~ fb_um_Meinung_zu_äußern + FBV_deabonnieren) -> hypo_c60

apastats::describe.r(hypo_c31, type="latex")
apastats::describe.r(hypo_c32, type="latex")
apastats::describe.r(hypo_c33, type="latex")
apastats::describe.r(hypo_c34, type="latex")
apastats::describe.r(hypo_c35, type="latex")

apastats::describe.r(hypo_c36, type="latex")
apastats::describe.r(hypo_c37, type="latex")
apastats::describe.r(hypo_c38, type="latex")
apastats::describe.r(hypo_c39, type="latex")
apastats::describe.r(hypo_c40, type="latex")

apastats::describe.r(hypo_c41, type="latex")
apastats::describe.r(hypo_c42, type="latex")
apastats::describe.r(hypo_c43, type="latex")
apastats::describe.r(hypo_c44, type="latex")
apastats::describe.r(hypo_c45, type="latex")

apastats::describe.r(hypo_c46, type="latex")
apastats::describe.r(hypo_c47, type="latex")
apastats::describe.r(hypo_c48, type="latex")
apastats::describe.r(hypo_c49, type="latex")
apastats::describe.r(hypo_c50, type="latex")

apastats::describe.r(hypo_c51, type="latex")
apastats::describe.r(hypo_c52, type="latex")
apastats::describe.r(hypo_c53, type="latex")
apastats::describe.r(hypo_c54, type="latex")
apastats::describe.r(hypo_c55, type="latex")

apastats::describe.r(hypo_c56, type="latex")
apastats::describe.r(hypo_c57, type="latex")
apastats::describe.r(hypo_c58, type="latex")
apastats::describe.r(hypo_c59, type="latex")
apastats::describe.r(hypo_c60, type="latex")

```


### Personality traits and Action against filter bubbles
```{r BigFive and avoidance strategies}
data %>% select("b5_n", "b5_o", "b5_e", "b5_a", "b5_c", "FBV_Loeschen", "FBV_Incognito", "FBV_Vielfalt_erzwingen", "FBV_Explorer", "FBV_deabonnieren") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ b5_e + FBV_Loeschen) -> hypo_c61
cor.test(data = corrdata, ~ b5_e + FBV_Incognito) -> hypo_c62
cor.test(data = corrdata, ~ b5_e + FBV_Vielfalt_erzwingen) -> hypo_c63
cor.test(data = corrdata, ~ b5_e + FBV_Explorer) -> hypo_c64
cor.test(data = corrdata, ~ b5_e + FBV_deabonnieren) -> hypo_c65

cor.test(data = corrdata, ~ b5_a + FBV_Loeschen) -> hypo_c66
cor.test(data = corrdata, ~ b5_a + FBV_Incognito) -> hypo_c67
cor.test(data = corrdata, ~ b5_a + FBV_Vielfalt_erzwingen) -> hypo_c68
cor.test(data = corrdata, ~ b5_a + FBV_Explorer) -> hypo_c69
cor.test(data = corrdata, ~ b5_a + FBV_deabonnieren) -> hypo_c70

cor.test(data = corrdata, ~ b5_c + FBV_Loeschen) -> hypo_c71
cor.test(data = corrdata, ~ b5_c + FBV_Incognito) -> hypo_c72
cor.test(data = corrdata, ~ b5_c + FBV_Vielfalt_erzwingen) -> hypo_c73
cor.test(data = corrdata, ~ b5_c + FBV_Explorer) -> hypo_c74
cor.test(data = corrdata, ~ b5_c + FBV_deabonnieren) -> hypo_c75

cor.test(data = corrdata, ~ b5_n + FBV_Loeschen) -> hypo_c76
cor.test(data = corrdata, ~ b5_n + FBV_Incognito) -> hypo_c77
cor.test(data = corrdata, ~ b5_n + FBV_Vielfalt_erzwingen) -> hypo_c78
cor.test(data = corrdata, ~ b5_n + FBV_Explorer) -> hypo_c79
cor.test(data = corrdata, ~ b5_n + FBV_deabonnieren) -> hypo_c80

cor.test(data = corrdata, ~ b5_o + FBV_Loeschen) -> hypo_c81
cor.test(data = corrdata, ~ b5_o + FBV_Incognito) -> hypo_c82
cor.test(data = corrdata, ~ b5_o + FBV_Vielfalt_erzwingen) -> hypo_c83
cor.test(data = corrdata, ~ b5_o + FBV_Explorer) -> hypo_c84
cor.test(data = corrdata, ~ b5_o + FBV_deabonnieren) -> hypo_c85

apastats::describe.r(hypo_c61, type="latex")
apastats::describe.r(hypo_c62, type="latex")
apastats::describe.r(hypo_c63, type="latex")
apastats::describe.r(hypo_c64, type="latex")
apastats::describe.r(hypo_c65, type="latex")

apastats::describe.r(hypo_c66, type="latex")
apastats::describe.r(hypo_c67, type="latex")
apastats::describe.r(hypo_c68, type="latex")
apastats::describe.r(hypo_c69, type="latex")
apastats::describe.r(hypo_c70, type="latex")

apastats::describe.r(hypo_c71, type="latex")
apastats::describe.r(hypo_c72, type="latex")
apastats::describe.r(hypo_c73, type="latex")
apastats::describe.r(hypo_c74, type="latex")
apastats::describe.r(hypo_c75, type="latex")

apastats::describe.r(hypo_c76, type="latex")
apastats::describe.r(hypo_c77, type="latex")
apastats::describe.r(hypo_c78, type="latex")
apastats::describe.r(hypo_c79, type="latex")
apastats::describe.r(hypo_c80, type="latex")

apastats::describe.r(hypo_c81, type="latex")
apastats::describe.r(hypo_c82, type="latex")
apastats::describe.r(hypo_c83, type="latex")
apastats::describe.r(hypo_c84, type="latex")
apastats::describe.r(hypo_c85, type="latex")

```

### What influences if someone takes active action?
```{r Influence of active action}
data %>% select("b5_n", "b5_o", "b5_e", "b5_a", "b5_c", "FiB_bewusstes_Vorgehen") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ b5_e + FiB_bewusstes_Vorgehen) -> hypo_c86
cor.test(data = corrdata, ~ b5_o + FiB_bewusstes_Vorgehen) -> hypo_c87
cor.test(data = corrdata, ~ b5_n + FiB_bewusstes_Vorgehen) -> hypo_c88
cor.test(data = corrdata, ~ b5_c + FiB_bewusstes_Vorgehen) -> hypo_c89
cor.test(data = corrdata, ~ b5_a + FiB_bewusstes_Vorgehen) -> hypo_c90

apastats::describe.r(hypo_c86, type="latex")
apastats::describe.r(hypo_c87, type="latex")
apastats::describe.r(hypo_c88, type="latex")
apastats::describe.r(hypo_c89, type="latex")
apastats::describe.r(hypo_c90, type="latex")


data %>% select(starts_with("fb_um"), "FiB_bewusstes_Vorgehen") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ fb_um_friends + FiB_bewusstes_Vorgehen) -> hypo_c91
cor.test(data = corrdata, ~ fb_um_newfriends + FiB_bewusstes_Vorgehen) -> hypo_c92
cor.test(data = corrdata, ~ fb_um_job + FiB_bewusstes_Vorgehen) -> hypo_c93
cor.test(data = corrdata, ~ fb_um_mich_informieren + FiB_bewusstes_Vorgehen) -> hypo_c94
cor.test(data = corrdata, ~ fb_um_andere_informieren + FiB_bewusstes_Vorgehen) -> hypo_c95
cor.test(data = corrdata, ~ fb_um_Meinung_zu_äußern + FiB_bewusstes_Vorgehen) -> hypo_c96

apastats::describe.r(hypo_c91, type="latex")
apastats::describe.r(hypo_c92, type="latex")
apastats::describe.r(hypo_c93, type="latex")
apastats::describe.r(hypo_c94, type="latex")
apastats::describe.r(hypo_c95, type="latex")
apastats::describe.r(hypo_c96, type="latex")

data %>% select(starts_with("FiB_")) %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ FiB_schon_gehört + FiB_bewusstes_Vorgehen) -> hypo_c97
cor.test(data = corrdata, ~ FiB_glaube_existiert + FiB_bewusstes_Vorgehen) -> hypo_c98
cor.test(data = corrdata, ~ FiB_betrifft_persönlich + FiB_bewusstes_Vorgehen) -> hypo_c99
cor.test(data = corrdata, ~ FiB_Problem + FiB_bewusstes_Vorgehen) -> hypo_c100
cor.test(data = corrdata, ~ FiB_interessante_Beiträge + FiB_bewusstes_Vorgehen) -> hypo_c101

apastats::describe.r(hypo_c97, type="latex")
apastats::describe.r(hypo_c98, type="latex")
apastats::describe.r(hypo_c99, type="latex")
apastats::describe.r(hypo_c100, type="latex")
apastats::describe.r(hypo_c101, type="latex")

AA_table2 <- data %>% select(starts_with("FiB")) %>% mutate_if(is.ordered, as.numeric) %>% apa.cor.table() %>% a_table()
AA_table3 <- data %>% select(starts_with("FBV_"), "FiB_bewusstes_Vorgehen") %>% mutate_if(is.ordered, as.numeric) %>% apa.cor.table() %>% a_table()
AA_table4 <- data %>% select("fb_um_friends", "fb_um_newfriends", "fb_um_job", "fb_um_mich_informieren", "fb_um_andere_informieren", "fb_um_Meinung_zu_äußern" ,"FiB_bewusstes_Vorgehen") %>% mutate_if(is.ordered, as.numeric) %>% apa.cor.table() %>% a_table()
AA_table5 <- data %>% select(starts_with("b5_") ,"FiB_bewusstes_Vorgehen") %>% mutate_if(is.ordered, as.numeric) %>% apa.cor.table() %>% a_table()
```

### General willingness to take active action and avoidance strategies?
```{r action and avoidance strategies}
data %>% select(starts_with("FBV"), "FiB_bewusstes_Vorgehen") %>% 
  mutate_if(is.ordered, as.numeric) -> corrdata

cor.test(data = corrdata, ~ FBV_Loeschen + FiB_bewusstes_Vorgehen) -> hypo_c200
cor.test(data = corrdata, ~ FBV_Incognito + FiB_bewusstes_Vorgehen) -> hypo_c201
cor.test(data = corrdata, ~ FBV_Vielfalt_erzwingen + FiB_bewusstes_Vorgehen) -> hypo_c202
cor.test(data = corrdata, ~ FBV_Explorer + FiB_bewusstes_Vorgehen) -> hypo_c203
cor.test(data = corrdata, ~ FBV_deabonnieren + FiB_bewusstes_Vorgehen) -> hypo_c204

apastats::describe.r(hypo_c200, type="latex")
apastats::describe.r(hypo_c201, type="latex")
apastats::describe.r(hypo_c202, type="latex")
apastats::describe.r(hypo_c203, type="latex")
apastats::describe.r(hypo_c204, type="latex")

AA_table6 <- data %>% select(starts_with("FBV_") ,"FiB_bewusstes_Vorgehen") %>% mutate_if(is.ordered, as.numeric) %>% apa.cor.table() %>% a_table()

```




