---
title: "Spiral of Silence"
author: "Patrick Halbach, André Calero Valdez"
date: "12 Dezember 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
library(sjlabelled)
```

First we clean our SPSS output files. For this purpose we remove identifying information..
```{r data-cleaning}
raw <- read_sav("data/SpiralofSilence_raw.sav")


# rename variables ---- 
codebook_filename <- "codebook.csv"

if(!file.exists(codebook_filename)){
  variable_names <- names(raw)
  label_names <- get_label(raw)

  codebook <- data.frame(variable_names, label_names)
  print("test")
  write_delim(codebook, path = codebook_filename, delim = ";")
} else {
  codebook <-read_delim(codebook_filename, delim=";")
}

  # Change variable labels to those from the codebook.csv
  names(raw) <- codebook$variable_names
  
  names(raw)
  

# select required variables ----
  raw[,c(-1:-10)] -> c_df
  
  c_df
  # factors and ordinal data
  c_df$Age <- as.numeric(c_df$Age)
  c_df$Gender
  
  
  # Function to convert factor variabls from surveymonkey spss file to usable factors
  convert_to_factor <- function(x, ordered = T, rev = F) {
      result <- factor(x, labels = get_labels(x), 
                       levels = 1:length(get_labels(x)), ordered = ordered )
      if(rev) {
        result <- fct_rev(result)
      }
      result
  }
  
  
  c_df <- c_df %>% mutate_at(vars(starts_with("big5")), convert_to_factor, rev = T )
  c_df <- c_df %>% mutate_at(vars(starts_with("fb_")), convert_to_factor, rev = T )  
  
  
  # filter incomplete responses
  
  codebook[22:27,]$label_names
  
  # calculate factors and scales
  
  key_list <- list(b5_o = list("big5_01", "big5_02"),
                   b5_e = list("-big5_03", "big5_04"),
                   b5_n = list("big5_05", "-big5_06"))
  
  scores <- psych::scoreItems(key_list, c_df, min = 1, max = 6, impute = "mean")  
  
  scores
  
  c_df <- c_df %>% cbind(scores$scores) 
  
  c_df %>% select(-starts_with("big5"))
  
  smusershigh <- filter(c_df,c_df$FrequencyOfSMUse > 4)
  smuserslow <- filter(c_df,c_df$FrequencyOfSMUse <= 4)
  
  
```
# Abstract
- In Social Media services such as Facebook, users encounter a wide range of other user's opinions on subjects concerning various topics
- Users have to evaluate the correctness and their opinion perceiption by themselves, leading to effects like the spiral silence and filter bubbles
- Occurence of Fake News and Social Bots who try to change Meinungsklima through Vortäuschen von Mehrheiten additionally increases difficulty of evaluation process
- Digital responsibility is key for handling these effects and forming an independent opinion
- We wanted to investigate, if the opinion of a user on certain topics changes, if he is confronted with negative or positive comments
- Mitläufereffekt, Schweigespirale auch in Social Media?
- Examined user factors: Gender, Big5 (Openness, extraversion, neuroticism), Frequency of Social Media Use
- Scenarios: 8 Facebook Posts, 4 topics: public toilets, Steuern für ungesunde Lebensmittel, Christiano Ronaldo, Rauchmelderpflicht
- Neutrale Themen vs. kontrovers diskutierte Themen, Vorabfrage der Meinung des Probanden zum jeweiligen Thema
- Bei positiver Einstellung: Anzeige eines Beitrags zu dem jeweiligen Thema mit einem positiven und vier negativen Kommentaren
- Am Ende: Erneute Abfrage der Einstellung des Probanden, hat er seine Meinung geändert?
- Hypotheses: User factors do influence possible opinion change
- Results: No measurable effects on most topics and user factors, only reliable correlation: opinion change on topic Ronaldo and openness
- Methodenreflexion: Very young aged (27.5), probably high experienced in Social Media Use
- Outlook: Opinion change could be dependent on emotional component of topic. Our prediction: Probanden lassen sich bei emotionaleren Themen tendenzielln nciht beeinflussen -> Probanden haben bereits eine Digitale Mündigkeit entwickelt